---
title: "mendr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mendr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mendr)
```

The goal of mendr is to simplify the task of creating a calendar of dates for a
recurring process.

A typical use case for this is to import the data produced by `mendr` into Microsoft
Planner via a Power Automate Flow. We describe this process below.

First, let's create a dataset. Here we need a list of tasks, and for each task an
offset relative to the first working day of the month. We count using index zero,
so the first working day of the month is 0, the second working day of the month is 
1 and so on. We can also work backwards: -1 is the first working day prior to the first
working day of the month.

After creating the dataset, we call `create_calendar()` in order to store a calendar
of non-working days that will be used to calculate the appropriate dates for our
schedule. By default, this stores known non-working days for Auckland Council
staff from Labour Day 2022 to Labour Day 2024.

```{r}
 tasks <- data.frame(
   tasks = c("Send email reminder", "Extract data", "Run report"),
   offsets = c(-2, 0, 1)
   )

create_calendar()
```

Although we manually created the data here, we would typically store this in an 
Excel spreadsheet and read it using the [readr](https://readr.tidyverse.org/)
package.

Next, let's convert our offsets into actual dates for the first three months of
2023.

```{r}
schedule <- create_schedule(
  schedule_data = tasks,
  starting_month = "2023-01",
  iterations = 3
  )

schedule
```

